\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-08-09 ase20/compiler.tex
[ASE] Updated Table 1
Updated report
[ASE20] Updated paper

\item \textbf{Abstract data types:} \( \ires \) supports only three abstract
data types: \( \code{Record} \) for mappings from values to values,
\( \code{List} \) for sequential data, and \( \code{Symbol} \) for singleton
data.  For example, ECMAScript environment records are represented as \(
\code{Record} \) from string values to addresses that represent the
bindings of the string values.
\end{itemize}
We define the syntax of \( \ires \) that has 15 kinds of instructions and 26 kinds
of expressions with the notation \( \irinst \) and \( \irexpr \), respectively.
We also formally define its operational semantics \(
\irstate \vdash \irinst \Rightarrow \irstate \) for instructions and
\( \irstate \vdash \irexpr \Rightarrow (\irvalue, \irstate) \) for expressions,
where \( \irstate \) denotes a state and \( \irvalue \) denotes a value.
For presentation brevity, we omit the formalization of \( \ires \) in this paper
and include it in a companion report\inred{\cite{report}}.

@@

\begin{table}[t]
  \centering
  \caption{General compile rules for ECMAScript}
  \label{table:rules}
\vspace*{-1em}
  \[
  \begin{array}{c?r|r|r|r|r|r}%|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c}{\code{Ref}}\\\hline
      \text{\# Rules}
      & \inred{17}
      & \inred{16}
      & \inred{8}
      & \inred{11}
      & \inred{33}
      & \inred{7}
    \end{array}
  \]
\vspace*{-2em}
\end{table}

@@

In ECMAScript, built-in objects are pre-defined functions with several
built-in functions.  For example, \( \code{Array} \)
is the constructor of array objects, and its prototype
\( \code{Array.prototype} \) has built-in functions for array objects.
For instance, \( \code{[1,2,3].flat()} \) calls the
\( \code{Array.prototype.flat} \) built-in function with the array
\( \code{[1,2,3]} \).  Because built-in functions are also abstract
algorithms, each of them is automatically converted to an \( \ires \)
function.  However, the structures of built-in objects should be
manually implemented.  Thus, we implemented built-in objects in Scala
and connected their properties with the extracted \( \ires \) functions.
%
Some built-in objects that are explicitly referenced in abstract
algorithms are intrinsic objects, which have their own
aliased names summarized in Table~7 of Section~6.1.7.4
\textsf{Well-Known Intrinsic Objects}.  We extracted the alias
into \textsf{Global Setting} to utilize it during evaluation.

>>>>

\item \textbf{Abstract data types:} \( \ires \) supports only three abstract
data types: \( \code{Record} \) for mappings from values to values,
\( \code{List} \) for sequential data, and \( \code{Symbol} \) for singleton
data.  For example, ECMAScript environment records are represented as \(
\code{Record} \) from string values to addresses that represent the
bindings of the string values.
\end{itemize}
We define the syntax of \( \ires \) that has 15 kinds of instructions and 26 kinds
of expressions with the notation \( \irinst \) and \( \irexpr \), respectively.
We also formally define its operational semantics \(
\irstate \vdash \irinst \Rightarrow \irstate \) for instructions and
\( \irstate \vdash \irexpr \Rightarrow (\irvalue, \irstate) \) for expressions,
where \( \irstate \) denotes a state and \( \irvalue \) denotes a value.
For presentation brevity, we omit the formalization of \( \ires \) in this paper
and include it in a companion report~\cite{report}.

@@

\begin{table}[t]
  \centering
  \caption{General compile rules for ECMAScript}
  \label{table:rules}
\vspace*{-1em}
  \[
  \begin{array}{c?r|r|r|r|r|r}%|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c}{\code{Ref}}\\\hline
      \text{\# Rules}
      & 21
      & 27
      & 16
      & 11
      & 34
      & 9
    \end{array}
  \]
\vspace*{-2em}
\end{table}

@@

In ECMAScript, built-in objects are pre-defined functions with several
built-in functions.  For example, \( \code{Array} \)
is the constructor of array objects, and its prototype
\( \code{Array.prototype} \) has built-in functions for array objects.
For instance, \( \code{[1,2,3].flat()} \) calls the
\( \code{Array.prototype.flat} \) built-in function with the array
\( \code{[1,2,3]} \).  Because built-in functions are also abstract
algorithms, each of them is automatically converted to an \( \ires \)
function.  However, the structures of built-in objects should be
manually implemented.  Thus, we implemented built-in objects in Scala
and connected their properties with the extracted \( \ires \) functions.
%
Some built-in objects that are explicitly referenced in abstract
algorithms are intrinsic objects, which have their own
aliased names summarized in
Table~7\footnote{https://www.ecma-international.org/ecma-262/10.0/\#sec-well-known-intrinsic-objects} of Section~6.1.7.4
\textsf{Well-Known Intrinsic Objects} in ES10.  We extracted the alias
into \textsf{Global Setting} to utilize it during evaluation.

### 2020-08-09 ase20/eval.tex
[ASE] Fixed a small typo in eval
[ASE20] Updated paper

We developed \( \tool \) as an open-source tool\footnote{The URL of the tool is
anonymized due to a double-blind review process.}, and evaluated the tool
based on the following research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Coverage:} How much percentage of 
the syntax and semantics does \( \tool \) automatically extract from ES7 to ES10?
\item RQ2. \textbf{Correctness:} Does \( \tool \) extract an IR-based formal
semantics from ECMAScript correctly?
\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
features ready for inclusion in the next ECMAScript (ES11)?
\end{itemize}

@@

To evaluate the correctness of \( \tool \), we checked whether the
extracted semantics from the latest ECMAScript (ES10) passes Test262
as of February 28, 2019, when ES10 was branched out.
To focus on the core language semantics of JavaScript, we completed
only necessary parts missing from the extracted AST-IR translator.
As Figure~\ref{fig:all-version}(a) shows, for the abstract algorithms
in ES10, 9,627 steps out of 10,101 steps are
automatically compiled by \textsf{Algorithm Compiler}.
Among the remaining 474 steps, we manually implemented all
missing steps for the core language semantics (137 steps) and
the essential parts of the built-in libraries (140 steps out of
337).  We also manually implemented \textsf{Global Setting}
as described in Section~\ref{sec:compiler-impl} for the core language features.
Note that we do not support minor language features such as the
non-strict mode, modules, early errors before actual execution, and
inessential built-in objects.
Among 35,990 tests in Test262, we filtered out 17,926
tests as summarized in Table~\ref{table:test262}.  To focus on ES10,
we excluded 7,038 tests for annexes, internationalization, and
in-progress features.  We also filted out 10,888 tests that use
minor language features.
Finally, for 18,064 applicable tests, the extracted semantics
failed for 1,709 tests.

@@

ES10-2 comes from the well-known dangling \code{else} problem
introduced in ALGOL 60~\cite{dangling-else}.  ES10 describes how to
parse it in prose: the \code{else} statement should be associated with
the nearest \code{if} statement.  Because it is written in prose
rather than in the ES10 grammar productions, it caused one test
failed.  We proposed a fix to revise the ambiguous grammar production,
and TC39 confirmed it on April 23, 2020.

ES10-3 is due to a misuse of the \code{=} operator for numbers.
In abstract algorithms, ``{\it x} = {\it y}'' denotes equality testing
for double-precision 64-bit binary format IEEE 754-2008 values;
thus, \mbox{``+0 = -0''} evaluates to true.  However, to check whether
{\it index} is exactly the same with -0,
{\bf StringGetOwnProperty} used \mbox{``{\it index} = -0''},
which is true even when {\it index} is +0.
It caused seven tests failed. We proposed a fix accepted on May 8, 2020.
Thus, ES10-3 existed for 1,802 days.

>>>>

We developed \( \tool \) as an open-source
tool\footnote{https://github.com/kaist-plrg/jiset}, and evaluated the tool based
on the following research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Coverage:} How much percentage of 
the syntax and semantics does \( \tool \) automatically extract from ES7 to ES10?
\item RQ2. \textbf{Correctness:} Does \( \tool \) extract an IR-based formal
semantics from ECMAScript correctly?
\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
features ready for inclusion in the next ECMAScript (ES11)?
\end{itemize}
We performed our experiments on a machine equipped with 4.2GHz Quad-Core Intel
Core i7 and 64GB of RAM.  On the machine, \( \tool \) took less than one minute
to extract IR-based semantics from a given ECMAScript.

@@

To evaluate the correctness of \( \tool \), we tested the extracted semantics
from the latest ECMAScript (ES10) by executing Test262 as of February 28, 2019,
when ES10 was branched out.
To focus on the core language semantics of JavaScript, we completed
only necessary parts missing from the extracted AST-IR translator.
As Figure~\ref{fig:all-version}(a) shows, for the abstract algorithms
in ES10, 9,627 steps out of 10,101 steps are
automatically compiled by \textsf{Algorithm Compiler}.
It fully covers 1,783 algorithms out of 2,026 abstract algorithms
and 243 algorithms are partially covered.
Among the remaining 474 steps, we manually implemented all
missing steps for the core language semantics (137 steps) and
the essential parts of the built-in libraries (140 steps out of 337).
Based on this manual implementation, 146 more abstract algorithms are fully covered.
We also manually implemented \textsf{Global Setting}
as described in Section~\ref{sec:compiler-impl} for the core language features.
Note that we do not support minor language features such as the
non-strict mode, modules, early errors before actual execution, and
inessential built-in objects.
Among 35,990 tests in Test262, we filtered out 17,926
tests as summarized in Table~\ref{table:test262}.  To focus on ES10,
we excluded 7,038 tests for annexes, internationalization, and
in-progress features.  We also filted out 10,888 tests that use
minor language features.
Finally, the extracted semantics took about three hours to evaluate 18,064
applicable tests and failed for 1,709 tests.

@@

ES10-2 comes from the well-known dangling \code{else} problem
introduced in ALGOL 60~\cite{dangling-else}.  ES10 describes how to
parse it in prose: the \code{else} statement should be associated with
the nearest \code{if} statement.  Because it is written in prose
rather than in the ES10 grammar productions, it caused one failed
test.  We proposed a fix to revise the ambiguous grammar production,
and TC39 confirmed it on April 23, 2020.

ES10-3 is due to a misuse of the \code{=} operator for numbers.
In abstract algorithms, ``{\it x} = {\it y}'' denotes equality testing
for double-precision 64-bit binary format IEEE 754-2008 values;
thus, \mbox{``+0 = -0''} evaluates to true.  However, to check whether
{\it index} is exactly the same with -0,
{\bf StringGetOwnProperty} used \mbox{``{\it index} = -0''},
which is true even when {\it index} is +0.
It caused seven failed tests. We proposed a fix accepted on May 7, 2020.
Thus, ES10-3 existed for 1,802 days.
